The Concurrent Calculi Formalisation Benchmark

### 2024-02-08 short-paper/short-paper.tex
Add references and clean up some wordings in coinduction paragraph.

\paragraph{Coinduction.} \todo{}

>>>>

\paragraph{Coinduction.} \todo{explain more what the challenge does.}
Coinduction is fundamental to establish properties of processes that
may never terminate, which is a typical situation. We base our challenge around
bisimulation: a coinductively established property for equating the
observed behaviour of potentially infinite processes.

Coinduction is widely supported in proof assistants.
Isabelle, Coq, and Abella seamlessly support coinductive definitions and reasoning.
Agda and Beluga support it through the convenient abstraction of co-patterns~\cite{Abel2013}.
Newer entrants to the field like the Lean proof assistant are working on adding a notion of coinduction to their system~\cite{Avigad2019,Keizer2023}.

As with most features, proof assistants support subtly different formalisms that enable different techniques and motivate this challenge.
Some systems provide more than one abstraction to use coinduction.
A good example of this are the parameterized coinduction~\cite{Hur2013} and interaction tree~\cite{Xia2019} libraries for Coq.

Common uses for coinduction are to define strong and weak versions of
bisimulation, barbed notions of bisimulation, prove trace equivalence,
etc.

In this challenge we study the notion of strong barbed bisimulation
over a fragment of the $\pi$-calculus.
